---
title: "Decision analysis"
output:
  html_document:
    df_print: paged
---

Analyze decisions across teams.

```{r setup, echo=FALSE,message=FALSE}

use_checkpoint = TRUE

s = Sys.info()
if (s['sysname'] == 'Darwin'){
  use_checkpoint = FALSE
}

if (use_checkpoint) {
  library(checkpoint)
  checkpointDir <- tempfile(pattern = "checkpoint")
  dir.create(checkpointDir)
  dir.create(file.path(checkpointDir, ".checkpoint"))
  checkpoint("2019-07-16", checkpointLocation = checkpointDir)
}

library(plyr)
library(tidyverse)
library(lmerTest)
library(lme4)
library(emmeans) 
library(pscl)
library(arm)
library(MuMIn)
library(multcomp)
library(multcompView)
library(optimx)
library(xtable)

basedir = Sys.getenv('NARPS_BASEDIR')
if (basedir == ""){
   # use default
   basedir = "/data"
}
cat(sprintf('using basedir: %s', basedir))

```

### Data setup 

Load the data and clean up some variables.  Requires metadata that is created by PrepareMetadata.ipynb

```{r loadData}
# load and clean up data
narps_df <- read_csv(paste(basedir,
                           'metadata/all_metadata.csv',
                           sep='/'))

narps_df <- narps_df %>% 
  mutate(Confidence = as.ordered(narps_df$Confidence))


narps_df$testing[is.na(narps_df$testing)] <- "Other"
narps_df$teamID = as.factor(narps_df$teamID)
narps_df$varnum = as.factor(narps_df$varnum)
```

Estimate correlation between reported smoothing kernel and estimated image smoothness.

```{r smoothCorr}
cor(narps_df$fwhm,narps_df$smoothing_coef,
    use='pairwise.complete',
    method='spearman')
```


### Models


First run mixed models across full dataset to assess overall effects on hypothesis acceptance. We use nlminb as the optimizer because the model failed to converge using the standard optimizer in lmer.

```{r fullModel}
hyp_df = narps_df %>% drop_na(fwhm,
                              used_fmriprep_data,
                              package,
                              testing)

m_hyp_full = glmer(Decision ~ varnum + fwhm + used_fmriprep_data + package + testing + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb')))

summary_full_model <- summary(m_hyp_full)
print(summary_full_model)

r.squaredGLMM(m_hyp_full)

```

#### Model comparisons

Model without hypothesis

```{r hypModel}
m_hyp_nohyp = glmer(Decision ~ fwhm + used_fmriprep_data + package + testing + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb')))
cat('\ntesting effect of smoothing\n')

anova_hyp<- anova(m_hyp_full,
                  m_hyp_nohyp,
                  test='Chisq')
print(anova_hyp)

# compute delta r-squared between this model and full model
delta_r2_hyp <- r.squaredGLMM(m_hyp_full) - r.squaredGLMM(m_hyp_nohyp) 
print(delta_r2_hyp)
```

Model without smoothing

```{r nosmoothModel}
m_hyp_nosmooth = glmer(Decision ~ varnum + used_fmriprep_data + package + testing + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb')))

cat('\ntesting effect of smoothing\n')

anova_smoothing <- anova(m_hyp_full,
                         m_hyp_nosmooth,
                         test='Chisq')
print(anova_smoothing)

emtrends(m_hyp_full,specs='fwhm',var='fwhm')

# compute delta r-squared between this model and full model
delta_r2_smoothing <- r.squaredGLMM(m_hyp_full) - r.squaredGLMM(m_hyp_nosmooth) 
print(delta_r2_smoothing)
```

Model without fmriprep

```{r noprepModel}
m_hyp_noprep = glmer(Decision ~ varnum + fwhm + package + testing + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb')))
cat('\ntesting effect of fmriprep\n')

anova_fmriprep <- anova(m_hyp_full,
                        m_hyp_noprep,
                        test='Chisq')
print(anova_fmriprep)

emmeans(m_hyp_full,'used_fmriprep_data')

# compute delta r-squared between this model and full model
delta_r2_fmriprep <- r.squaredGLMM(m_hyp_full) - r.squaredGLMM(m_hyp_noprep) 

print(delta_r2_fmriprep)
```

```{r nopackageModel}


m_hyp_nopackage = glmer(Decision ~ varnum + used_fmriprep_data + fwhm + testing + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb'))) 
cat('\ntesting effect of package\n')

anova_package <- anova(m_hyp_full,
                       m_hyp_nopackage,
                       test='Chisq')
print(anova_package)

leastsquare = emmeans(m_hyp_full,
                      'package')
multcomp::cld(leastsquare, 
    level=.05)

# compute delta r-squared between this model and full model
delta_r2_package <- r.squaredGLMM(m_hyp_full) - r.squaredGLMM(m_hyp_nopackage)
print(delta_r2_package)
```

```{r notestingModel}
  
m_hyp_notesting = glmer(Decision ~ varnum + used_fmriprep_data + fwhm + package + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb')))   
cat('\ntesting effect of testing\n')

anova_testing <- anova(m_hyp_full,
                       m_hyp_notesting,test='Chisq')
print(anova_testing)

leastsquare = emmeans(m_hyp_full,
                      'testing')
multcomp::cld(leastsquare, 
    level=.05)

# compute delta r-squared between this model and full model
delta_r2_testing <- r.squaredGLMM(m_hyp_full) - r.squaredGLMM(m_hyp_notesting)
print(delta_r2_testing)
```

Full model using specified smoothing filter rather than estimated smoothness.

```{r kernelModel}
m_hyp_full_tsc = glmer(Decision ~ varnum + smoothing_coef + used_fmriprep_data + package + testing + (1|teamID),
            data = hyp_df,family=binomial,
            control = glmerControl(optimizer ='optimx', 
                                   optCtrl=list(method='nlminb')))
summary(m_hyp_full_tsc)

```


For each hypothesis, we ask whether decisions are associated with fwhm and use of fmriprep.  None of these survive Bonferroni correction.

```{r runModelsFunction}

runModels = function(hyp){
  pvals = c()
  hyp_df = narps_df %>% 
    filter(varnum==!!hyp) %>% drop_na(fwhm,
                                      used_fmriprep_data,
                                      package,
                                      testing)

  m_hyp_full = bayesglm(Decision ~ fwhm + used_fmriprep_data + package + testing,
                   data = hyp_df,family=binomial)
  
  m_hyp_nosmooth = bayesglm(Decision ~ used_fmriprep_data + package + testing,
                   data = hyp_df,family=binomial)
  #cat('testing effect of smoothing\n')
  a = anova(m_hyp_full,
            m_hyp_nosmooth,
            test='Chisq')
  pvals = c(pvals,unlist(a)['Pr(>Chi)2'])
  
  m_hyp_noprep = bayesglm(Decision ~ fwhm + package + testing,
                   data = hyp_df,family=binomial)
  #cat('testing effect of fmriprep\n')
  a=anova(m_hyp_full,m_hyp_noprep,test='Chisq')
  pvals = c(pvals,unlist(a)['Pr(>Chi)2'])
  
  m_hyp_nopackage = bayesglm(Decision ~ used_fmriprep_data + fwhm + testing,
                   data = hyp_df,family=binomial)
  #cat('testing effect of package\n')
  a=anova(m_hyp_full,
          m_hyp_nopackage,
          test='Chisq')
  pvals = c(pvals,unlist(a)['Pr(>Chi)2'])
  
  
  m_hyp_notesting = bayesglm(Decision ~ used_fmriprep_data + fwhm + package,
                   data = hyp_df,family=binomial)
  #cat('testing effect of testing\n')
  a=anova(m_hyp_full,
          m_hyp_notesting,
          test='Chisq')
  pvals = c(pvals,unlist(a)['Pr(>Chi)2'])
  return(pvals)
}
```



```{r runAllModels}
all_pvals = c()
for (hyp in 1:9){
  pv = runModels(hyp)
  all_pvals = rbind(all_pvals,pv)
}

```

### Plot the data

#### decision vs. software package

```{r plotSoftware}
decisionSummary_package <- narps_df %>%
  drop_na(package) %>%
  group_by(package,varnum) %>%
  summarize(meanAccept = mean(Decision),
            numTeams = n()) 

ggplot(decisionSummary_package,
       aes(varnum,meanAccept,color=package,group=package)) +
  geom_line(aes(size=numTeams))

```


#### decision vs. use of fMRIprep

```{r plotfMRIPrep}
decisionSummary_fmriprep <- narps_df %>%
  drop_na(used_fmriprep_data) %>%
  group_by(used_fmriprep_data,varnum) %>%
  summarize(meanAccept = mean(Decision),
            numTeams = n()) 

ggplot(decisionSummary_fmriprep,
       aes(varnum,meanAccept,
           color=used_fmriprep_data, 
           group=used_fmriprep_data)) + 
  geom_line()

```


#### decision vs. Effects of smoothing

First we examine the effect of actual image smoothness, estimated using FSL.

```{r plotEstimatedSmoothness}
decisionSummary_smoothing <- narps_df %>%
  drop_na(fwhm) %>%
  mutate(Decision_factor = as.factor(Decision)) %>%
  group_by(Decision_factor,varnum) %>%
  summarize(meanFWHM = mean(fwhm),
            numTeams = n()) 

ggplot(decisionSummary_smoothing,
       aes(varnum,meanFWHM,
           color=Decision_factor,
           group=Decision_factor)) +
  geom_line() 
  

```


effect of the applied smoothing kernel.

```{r plotAppliedSmoothing}
decisionSummary_smoothingkernel <- narps_df %>%
  drop_na(fwhm) %>%
  mutate(Decision_factor = as.factor(Decision)) %>%
  group_by(Decision_factor,varnum) %>%
  summarize(meanAppliedFWHM = mean(smoothing_coef),
            numTeams = n()) 

ggplot(decisionSummary_smoothingkernel,
       aes(varnum,meanAppliedFWHM,
           color=Decision_factor)) +
  geom_line() 

```


### Examine effects of various factors on pattern distance

```{r loadPatternDistance}

patterndist_df = read_csv(paste(basedir,
          'metadata/median_pattern_distance.csv',
          sep='/'),skip=0)
names(patterndist_df)=c('teamID','mean_distance')

merged_df = join(patterndist_df,narps_df %>% 
                   filter(varnum==1),by=c('teamID'))
```

### fit model

```{r r2z}
r2z = function(r){
    # fisher transform
    z=0.5*log((1.0+r)/(1.0-r))
    z[is.na(z)]=0
    return(z)
}
```


```{r fitPatternDistanceModel}

merged_df <- merged_df %>%
  mutate(z_mean_distance = r2z(mean_distance))

merged_df = merged_df %>% 
  drop_na(fwhm,used_fmriprep_data,package,testing)

dist_hyp_full = lm(z_mean_distance ~ fwhm + used_fmriprep_data + package + testing,
            data = merged_df)

s <- summary(dist_hyp_full)
print(s)

```

```{r fitnoSmoothDistanceModel}
dist_hyp_nosmooth <- lm(z_mean_distance ~ used_fmriprep_data + package + testing,
            data = merged_df)

cat('\ntesting effect of smoothing\n')

anova(dist_hyp_full,
      dist_hyp_nosmooth,
      test='Chisq')

emtrends(dist_hyp_full,specs='fwhm',var='fwhm')
s$r.squared - summary(dist_hyp_nosmooth)$r.squared

```

```{r fitNoPrepDistanceModel}
dist_hyp_noprep = lm(z_mean_distance ~ fwhm + package + testing,
            data = merged_df)
cat('\ntesting effect of fmriprep\n')

anova(dist_hyp_full,
      dist_hyp_noprep,
      test='Chisq')

emmeans(dist_hyp_full,'used_fmriprep_data')
s$r.squared - summary(dist_hyp_noprep)$r.squared

```

```{r fitNoHypDistanceModel}
dist_hyp_nopackage = lm(z_mean_distance ~ used_fmriprep_data + fwhm + testing,
            data = merged_df) 
cat('\ntesting effect of package\n')

anova(dist_hyp_full,
      dist_hyp_nopackage,
      test='Chisq')
s$r.squared - summary(dist_hyp_nopackage)$r.squared
leastsquare = emmeans(dist_hyp_full,'package')
multcomp::cld(leastsquare, 
    level=.05)


```

```{r fitNoTestingDistanceModel}
dist_hyp_notesting = lm(z_mean_distance ~ used_fmriprep_data + fwhm + package,
            data = merged_df)   
cat('\ntesting effect of testing\n')

anova(dist_hyp_full,
      dist_hyp_notesting,
      test='Chisq')
s$r.squared - summary(dist_hyp_notesting)$r.squared

leastsquare = emmeans(dist_hyp_full,
                      'testing')
multcomp::cld(leastsquare, 
    level=.05)


```

Make supplementary table 5

```{r mkSuppTable5}

df_SuppTable4 <- data.frame(
  Effects = c('Hypothesis', 
              'Smoothing', 
              'Used fMRIprep data', 
              'Software package', 
              'Multiple testing correction')) %>%
  mutate(ChiSquared = NA,
         Pvalue = NA,
         delta_r2 = NA)

df_SuppTable4[1,2:4] = c(anova_hyp$`Chisq`[2],
                         anova_hyp$`Pr(>Chisq)`[2],
                         delta_r2_hyp[2,1]
                         )
df_SuppTable4[2,2:4] = c(anova_smoothing$`Chisq`[2],
                         anova_smoothing$`Pr(>Chisq)`[2],
                         delta_r2_smoothing[2,1]
                         )
df_SuppTable4[3,2:4] = c(anova_fmriprep$`Chisq`[2],
                         anova_fmriprep$`Pr(>Chisq)`[2],
                         delta_r2_fmriprep[2,1]
                         )
df_SuppTable4[4,2:4] = c(anova_package$`Chisq`[2],
                         anova_package$`Pr(>Chisq)`[2],
                         delta_r2_package[2,1]
                         )
df_SuppTable4[5,2:4] = c(anova_testing$`Chisq`[2],
                         anova_testing$`Pr(>Chisq)`[2],
                         delta_r2_testing[2,1]
                         )

print(df_SuppTable4)

write.table(df_SuppTable4,
            file=paste(basedir,"SuppTable4.txt",sep='/'))

tab_latex = print(xtable(df_SuppTable4, 
             type = "latex", 
             digits=c(0,0,2,3,2)),
      floating=FALSE,
      latex.environments=NULL,
      booktabs=TRUE)

latex_preamble=c('\\documentclass[11pt, oneside]{article}',
'\\title{Supplementary Table 4}',
'\\date{}',
'\\usepackage{booktabs}',
'\\begin{document}',
'\\maketitle')

if (TRUE) {
fileConn<-file(paste(basedir,"SuppTable4.tex",sep='/'))
writeLines(c(latex_preamble,tab_latex,c('\\end{document}')), fileConn)
#writeLines(tab_latex, fileConn)
close(fileConn)

# leave this out so that we don't have to install tex within docker
#texi2dvi(paste(basedir,"SuppTable4.tex",sep='/'),
#         clean = TRUE)
}

```


```{r tmpCleanup}
if (use_checkpoint){
  unlink(checkpointDir, recursive = TRUE)
}
```

