---
title: "NARPS Prediction Market Analyses"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---

This was adapted from Analyses.R provided by Felix Holzmeister.

## Setup Working Directories

```{r setup}


basedir = Sys.getenv('NARPS_BASEDIR')
if (basedir == ""){
  # use default
  basedir = "/data"
}

use_checkpoint = TRUE

s = Sys.info()
if (s['sysname'] == 'Darwin'){
  use_checkpoint = FALSE
}

if (use_checkpoint) {
  library(checkpoint)
  checkpointDir <- '/checkpoint'
  checkpoint("2019-08-13", checkpointLocation = checkpointDir)
  }

library(dplyr)
library(tidyr)

output_dir <- paste(basedir,'PredictionMarkets',sep='/')
proc <- paste(output_dir, 'Processed',sep='/')
if (!dir.exists(proc)){
  stop('proc dir does not exist!')
}
figdir <- paste(output_dir, 'Figures',sep='/')
if (!dir.exists(figdir)){
  dir.create(figdir)
}

```

## Prepare Data

```{r prepareData}
load(paste(proc, "Prices.RData", sep='/'))
load(paste(proc, "Fundamentals.RData", sep='/'))

Data <- merge(Prices, 
              fundamental, 
              by="hid")

Data <- reshape(Data, 
                direction = "wide", 
                v.names = "price", 
                timevar = "teams", 
                idvar = "hid")



```

Make table for Supplementary Materials

```{r}
bracket = function(s) {sprintf('[%s]', s)}

supptable_df <- Data %>%
  mutate(fv = formatC(Data$fv, digits=2,format='f'),
         CI_lower = formatC(Data$fv_95l, digits=2,format='f'),
         CI_upper = formatC(Data$fv_95u, digits=2,format='f'),
         nt_exceed = as.integer((Data$price.0 > Data$fv_95u) | (Data$price.0 < Data$fv_95l)),
         t_exceed = as.integer((Data$price.1 > Data$fv_95u) | (Data$price.1 < Data$fv_95l)))

supptable_df <- supptable_df %>%
  mutate(
         NonTeams = price.0,
         NonTeamsOutside = recode(supptable_df$nt_exceed, `0` = '', `1` = '*'),
         Teams = price.1,
         TeamsOutside = recode(supptable_df$t_exceed, `0` = '', `1` = '*')) %>%
  unite('CI', CI_lower:CI_upper, sep='-') %>%
  mutate(CI = sapply(CI,bracket)) %>%
  dplyr::select(-fv_95l, -fv_95u, -price.0, -price.1, -t_exceed, -nt_exceed)

write.table(supptable_df,
            file=paste(output_dir,
                       "Figures/SuppTable_MarketResults.txt",sep='/'),
            quote=FALSE, col.names=FALSE,sep='\t')
```

## Spearman Correlations: Market Beliefs

### Fundamental Value vs. Market Belief 'Non-Teams'

```{r}
sc_fv_nt <- cor.test(x=Data$price.0, 
                     y=Data$fv, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_fv_nt$estimate, 
    "p-value:", sc_fv_nt$p.value)

```

### Fundamental Value vs. Market Belief 'Teams'

```{r}
sc_fv_tt <- cor.test(x=Data$price.1, 
                     y=Data$fv, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_fv_tt$estimate, 
    "p-value:", sc_fv_tt$p.value)

```

### Market Belief 'Non-Teams' vs. Market Belief 'Teams' 

```{r}
sc_nt_tt <- cor.test(x=Data$price.0, 
                     y=Data$price.1, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_nt_tt$estimate, 
    "p-value:", sc_nt_tt$p.value)


```

## Wilcoxon signed-rank tests: Market beliefs


### Fundamental Value vs. Market Belief for 'Non-Teams'

```{r wt_fv_nt}
wt_fv_nt <- wilcox.test(Data$price.0, 
                        Data$fv, 
                        alternative="two.sided", 
                        paired=TRUE, 
                        exact=TRUE)
cat("z-value:", abs(qnorm(wt_fv_nt$p.value/2)), 
    "p-value:", wt_fv_nt$p.value)

```

### Fundamental Value vs. Market Belief for 'Teams'

```{r wt_fv_tt}
wt_fv_tt <- wilcox.test(Data$price.1, 
                        Data$fv, 
                        alternative="two.sided",
                        paired=TRUE,
                        exact=TRUE) 
cat("z-value:", abs(qnorm(wt_fv_tt$p.value/2)), 
    "p-value:", wt_fv_tt$p.value)

```

### Market Belief 'Non-Teams' vs. Market Belief 'Teams'

```{r wt_nt_tt}
wt_nt_tt <- wilcox.test(Data$price.0, 
                        Data$price.1, 
                        alternative="two.sided", 
                        paired=TRUE, 
                        exact=TRUE)  
cat("z-value:", abs(qnorm(wt_nt_tt$p.value/2)), 
    "p-value:", wt_nt_tt$p.value)


```


## Team statistics

### Prepare Data

```{r prepData2}
load(paste(proc, "Holdings.RData", sep='/'))
load(paste(proc, "TeamResults.RData", sep='/'))
load(paste(proc, "Fundamentals.RData", sep='/'))

Data <- merge(Holdings,
              TeamResults,
              by=c("uid","hid","teams"),
              all.x = TRUE)

Data <- merge(Data, 
              fundamental, 
              by="hid")

Data<-Data[!(Data$teams == 0),]
Data<-Data[!(Data$shares == 0),]

```


```{r}

Data$consistent <- 0
Data$consistent <- ifelse(Data$decision==1 & Data$shares>0,1,Data$consistent)
Data$consistent <- ifelse(Data$decision==0 & Data$shares<0,1,Data$consistent)

wt_results_df <- data.frame(Hypothesis=c(1:9)) %>%
  mutate(rho = NA,
         pValue = NA,
         frac = NA,
         z = NA,
         z_pval = NA,
         inc = NA,
         con = NA)

for (i in 1:9) {
  
  data_wt <- Data[(Data$hid == i),]
  
  # Spearman correlation: 
  # Fundamental Value vs. Market Belief
  corr <- cor.test(x=data_wt$shares, 
                   y=data_wt$decision,
                   method='spearman', 
                   exact=FALSE)
  wt_results_df[i,'rho'] <- formatC(corr$estimate,digits=2,format='f')
  wt_results_df[i,'pValue'] <- formatC(corr$p.value,digits=3,format='f')
  data_wt$testval <- 0.5
  data_wt$test <- data_wt$consistent - 0.5
  a <- as.data.frame(table(sign(data_wt$test)))
  
  a$total <- sum(a$Freq)
  a$frac  <- a$Freq/a$total
  
  # Wilcoxon signed-rank test: 
  # Final Holdings Consistent with Team Result    
  wt <- wilcox.test(data_wt$consistent, 
                    data_wt$testval, 
                    alternative="two.sided",
                    paired=TRUE,
                    exact=FALSE)      
  
  wt_results_df[i,'frac'] <- formatC(a[a$Var1==1, "frac"],digits=2,format='f')
  wt_results_df[i,'z'] <- formatC(abs(qnorm(wt$p.value/2)),digits=2,format='f')
  wt_results_df[i,'z_pval'] <- formatC(wt$p.value/2,digits=3,format='f')
  wt_results_df[i,'inc'] <- formatC(mean(data_wt[data_wt$consistent==0,"shares"]),digits=2,format='f')
  wt_results_df[i,'con'] <- formatC(mean(data_wt[data_wt$consistent==1,"shares"]),digits=2,format='f')
  

}
```

### Make supplementary tables

```{r}
names(wt_results_df) <- c('Hypothesis #',
                          'Spearman rho',
                          'p-value',
                          'Share of consistent holdings',
                          'Z (signed rank test)',
                          'p-value (signed rank test)',
                          'Average holdings if consistent',
                          'Average holdings if inconsistent')
write.table(t(wt_results_df), file=paste(output_dir,
                       "Figures/SuppTable_HoldingStats.txt",sep='/'),
            quote=FALSE, col.names=FALSE,sep='\t')
wt_results_df
```


## Panel regressions                                      

```{r}

load(paste(proc, "BalancedPanel.RData", sep='/'))

m1 <- lm(ae~time+teams, data = BalancedPanel)
s1 <- summary(m1, robust=TRUE)

sink(paste(figdir,'lm1_summary.txt', sep='/'))
print(s1)
sink() 

m2 <- lm(ae~time+teams+time:teams, data = BalancedPanel)
s2 <- summary(m2, robust=TRUE)

sink(paste(figdir,'lm2_summary.txt', sep='/'))
print(s2)
sink() 

```

### Make supplementary table for panel regressions

```{r}
panelreg_df <- data.frame(effect = c('Intercept',
                                     'Time',
                                     'Teams',
                                     'Time X Teams')) %>%
  mutate(Beta_1=NA, 
         t_1 = NA,
         pValue_1=NA,
         Beta_2=s2$coefficients[1:4,1], 
         t_2 = s2$coefficients[1:4,3],
         pValue_2=s2$coefficients[1:4,4])
panelreg_df[1:3, 'Beta_1'] = s1$coefficients[1:3,1]
panelreg_df[1:3, 't_1'] = s1$coefficients[1:3,3]
panelreg_df[1:3, 'pValue_1'] = s1$coefficients[1:3,4]

panelreg_df
```


