---
title: "NARPS Prediction Market Analyses"
output:
  word_document: default
  pdf_document: default
  html_notebook: default
---

This was adapted from Analyses.R provided by Felix Holzmeister.

## Setup Working Directories

```{r setup}


basedir = Sys.getenv('NARPS_BASEDIR')
if (basedir == ""){
  # use default
  basedir = "/data"
}

use_checkpoint = TRUE

s = Sys.info()
if (s['sysname'] == 'Darwin'){
  use_checkpoint = FALSE
}

if (use_checkpoint) {
  library(checkpoint)
  checkpointDir <- '/checkpoint'
  checkpoint("2019-08-13", checkpointLocation = checkpointDir)
  }

library(plyr)
library(dplyr)
library(tidyr)
library(readr)

output_dir <- paste(basedir,'PredictionMarkets',sep='/')
proc <- paste(output_dir, 'Processed',sep='/')
if (!dir.exists(proc)){
  stop('proc dir does not exist!')
}
figdir <- paste(output_dir, 'Figures',sep='/')
if (!dir.exists(figdir)){
  dir.create(figdir)
}

```

## Prepare Data

```{r prepareData}
load(paste(proc, "Prices.RData", sep='/'))
load(paste(proc, "Fundamentals.RData", sep='/'))

Data <- merge(Prices, 
              fundamental, 
              by="hid")

Data <- reshape(Data, 
                direction = "wide", 
                v.names = "price", 
                timevar = "teams", 
                idvar = "hid")



```

Make table for Supplementary Materials

```{r}
bracket = function(s) {sprintf('[%s]', s)}

supptable_df <- Data %>%
  mutate(FV = formatC(Data$fv, digits=2,format='f'),
         CI_lower = formatC(Data$fv_95l, digits=2,format='f'),
         CI_upper = formatC(Data$fv_95u, digits=2,format='f'),
         nt_exceed = as.integer((Data$price.0 > Data$fv_95u) | (Data$price.0 < Data$fv_95l)),
         t_exceed = as.integer((Data$price.1 > Data$fv_95u) | (Data$price.1 < Data$fv_95l)))

supptable_df <- supptable_df %>%
  mutate(
         NonTeams = price.0,
         NonTeamsOutside = recode(supptable_df$nt_exceed, `0` = '', `1` = '*'),
         Teams = price.1,
         TeamsOutside = recode(supptable_df$t_exceed, `0` = '', `1` = '*')) %>%
  unite('CI', CI_lower:CI_upper, sep='-') %>%
  mutate(CI = sapply(CI,bracket)) %>%
  unite('Non-teams FV', NonTeams:NonTeamsOutside, sep=' ') %>%
  unite('Teams FV', Teams:TeamsOutside, sep=' ') %>%
  dplyr::select(-fv,-fv_95l, -fv_95u, -price.0, -price.1, -t_exceed, -nt_exceed, -hypothesis) 
supptable_df <- supptable_df %>%
  rename(`Hyp #` = hid) 
write.table(supptable_df,
            file=paste(output_dir,
                       "Figures/SuppTable_MarketResults.tsv",sep='/'),
            quote=FALSE, col.names=TRUE,sep='\t', row.names=FALSE)
```

## Spearman Correlations: Market Beliefs

### Fundamental Value vs. Market Belief 'Non-Teams'

```{r}
sc_fv_nt <- cor.test(x=Data$price.0, 
                     y=Data$fv, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_fv_nt$estimate, 
    "p-value:", sc_fv_nt$p.value)

```

### Fundamental Value vs. Market Belief 'Teams'

```{r}
sc_fv_tt <- cor.test(x=Data$price.1, 
                     y=Data$fv, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_fv_tt$estimate, 
    "p-value:", sc_fv_tt$p.value)

```

### Market Belief 'Non-Teams' vs. Market Belief 'Teams' 

```{r}
sc_nt_tt <- cor.test(x=Data$price.0, 
                     y=Data$price.1, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_nt_tt$estimate, 
    "p-value:", sc_nt_tt$p.value)


```

## Wilcoxon signed-rank tests: Market beliefs


### Fundamental Value vs. Market Belief for 'Non-Teams'

```{r wt_fv_nt}
wt_fv_nt <- wilcox.test(Data$price.0, 
                        Data$fv, 
                        alternative="two.sided", 
                        paired=TRUE, 
                        exact=TRUE)
cat("z-value:", abs(qnorm(wt_fv_nt$p.value/2)), 
    "p-value:", wt_fv_nt$p.value)

```

### Fundamental Value vs. Market Belief for 'Teams'

```{r wt_fv_tt}
wt_fv_tt <- wilcox.test(Data$price.1, 
                        Data$fv, 
                        alternative="two.sided",
                        paired=TRUE,
                        exact=TRUE) 
cat("z-value:", abs(qnorm(wt_fv_tt$p.value/2)), 
    "p-value:", wt_fv_tt$p.value)

```

### Market Belief 'Non-Teams' vs. Market Belief 'Teams'

```{r wt_nt_tt}
wt_nt_tt <- wilcox.test(Data$price.0, 
                        Data$price.1, 
                        alternative="two.sided", 
                        paired=TRUE, 
                        exact=TRUE)  
cat("z-value:", abs(qnorm(wt_nt_tt$p.value/2)), 
    "p-value:", wt_nt_tt$p.value)


```


## Team statistics

### Prepare Data

```{r prepData2}
load(paste(proc, "Holdings.RData", sep='/'))
load(paste(proc, "TeamResults.RData", sep='/'))
load(paste(proc, "Fundamentals.RData", sep='/'))

Data <- merge(Holdings,
              TeamResults,
              by=c("uid","hid","teams"),
              all.x = TRUE)

Data <- merge(Data, 
              fundamental, 
              by="hid")

Data<-Data[!(Data$teams == 0),]
Data<-Data[!(Data$shares == 0),]

```


```{r}

Data$consistent <- 0
Data$consistent <- ifelse(Data$decision==1 & Data$shares>0,1,Data$consistent)
Data$consistent <- ifelse(Data$decision==0 & Data$shares<0,1,Data$consistent)

wt_results_df <- data.frame(Hypothesis=c(1:9)) %>%
  mutate(rho = NA,
         pValue = NA,
         frac = NA,
         z = NA,
         z_pval = NA,
         inc = NA,
         con = NA)

for (i in 1:9) {
  
  data_wt <- Data[(Data$hid == i),]
  
  # Spearman correlation: 
  # Fundamental Value vs. Market Belief
  corr <- cor.test(x=data_wt$shares, 
                   y=data_wt$decision,
                   method='spearman', 
                   exact=FALSE)
  wt_results_df[i,'rho'] <- formatC(corr$estimate,digits=2,format='f')
  wt_results_df[i,'pValue'] <- formatC(corr$p.value,digits=3,format='f')
  data_wt$testval <- 0.5
  data_wt$test <- data_wt$consistent - 0.5
  a <- as.data.frame(table(sign(data_wt$test)))
  
  a$total <- sum(a$Freq)
  a$frac  <- a$Freq/a$total
  
  # Wilcoxon signed-rank test: 
  # Final Holdings Consistent with Team Result    
  wt <- wilcox.test(data_wt$consistent, 
                    data_wt$testval, 
                    alternative="two.sided",
                    paired=TRUE,
                    exact=FALSE)      
  
  wt_results_df[i,'frac'] <- formatC(a[a$Var1==1, "frac"],digits=2,format='f')
  wt_results_df[i,'z'] <- formatC(abs(qnorm(wt$p.value/2)),digits=2,format='f')
  wt_results_df[i,'z_pval'] <- formatC(wt$p.value/2,digits=3,format='f')
  wt_results_df[i,'inc'] <- formatC(mean(data_wt[data_wt$consistent==0,"shares"]),digits=2,format='f')
  wt_results_df[i,'con'] <- formatC(mean(data_wt[data_wt$consistent==1,"shares"]),digits=2,format='f')
  

}
```

### Make supplementary tables

```{r}
names(wt_results_df) <- c('Hypothesis #',
                          'Spearman rho',
                          'p-value',
                          'Share of consistent holdings',
                          'Z (signed rank test)',
                          'p-value (signed rank test)',
                          'Average holdings if consistent',
                          'Average holdings if inconsistent')
write.table(t(wt_results_df), file=paste(output_dir,
                       "Figures/SuppTable_HoldingStats.tsv",sep='/'),
            quote=FALSE, row.names=TRUE,col.names=FALSE, sep='\t')
wt_results_df
```


## Panel regressions                                      

```{r}

load(paste(proc, "BalancedPanel.RData", sep='/'))

m1 <- lm(ae~time+teams, data = BalancedPanel)
s1 <- summary(m1, robust=TRUE)

sink(paste(figdir,'lm1_summary.txt', sep='/'), append = FALSE, type = "output")
print(s1)
sink() 

m2 <- lm(ae~time+teams+time:teams, data = BalancedPanel)
s2 <- summary(m2, robust=TRUE)

sink(paste(figdir,'lm2_summary.txt', sep='/'), append = FALSE, type = "output")
print(s2)
sink() 

```

### Make supplementary table for panel regressions

```{r}
panelreg_df <- data.frame(effect = c('Intercept',
                                     'Time',
                                     'Teams',
                                     'Time X Teams',
                                     '--------',
                                     'Adjusted R-squared'))

panelreg_df[1:4, 'Beta_2'] = formatC(s2$coefficients[1:4,1], digits=2,format='f')
panelreg_df[1:4, 't_2'] = formatC(s2$coefficients[1:4,3], digits=2,format='f')
panelreg_df[1:4, 'pValue_2'] = formatC(s2$coefficients[1:4,4], digits=3,format='f')
panelreg_df[1:3, 'Beta_1'] = formatC(s1$coefficients[1:3,1], digits=2,format='f')
panelreg_df[1:3, 't_1'] = formatC(s1$coefficients[1:3,3], digits=2,format='f')
panelreg_df[1:3, 'pValue_1'] = formatC(s1$coefficients[1:3,4], digits=3,format='f')
panelreg_df[6, 'pValue_1'] = formatC(s1$adj.r.squared, digits=2,format='f')
panelreg_df[6, 'pValue_2'] = formatC(s2$adj.r.squared, digits=2,format='f')
panelreg_df[is.na(panelreg_df)]=""
names(panelreg_df) = c('Effect', 'Beta (full model)', 't (full model)', 'p (full model)', 'Beta (no interaction)', 't (no interaction)', 'p (no interaction)')
write.table(panelreg_df,
            file=paste(output_dir,
                  "Figures/SuppTable_PanelRegressions.tsv",sep='/'),
            quote=FALSE, col.names=TRUE,sep='\t', row.names=FALSE)

```

## Make market details figure

 
```{r}
load(paste(proc, "Transactions.RData", sep='/'))

trans_summary <- Transactions %>%
  mutate(teams = recode_factor(Transactions$teams, `0`='Non-teams', `1`='Teams')) %>%
  group_by(hid, teams) %>%
  summarize(`Tokens invested`=mean(abs(investment)),
            `Volume (shares)`=mean(abs(shares)),
            `# Transactions`=length(unique(tid)),
            `# Traders`=length(unique(uid)))

#
# spread out team/nonteams
# this is kludgey - sorry, sometimes that's the fastest way to 
# do things

trans_summary_tokens <- trans_summary %>%
  dplyr::select(hid, teams,`Tokens invested` ) %>%
  spread(teams, `Tokens invested`) 
names(trans_summary_tokens) = c('hyp', 'Tokens invested (Non-teams)', 'Tokens invested (Teams)')
trans_summary_volume <- trans_summary %>%
  dplyr::select(hid, teams,`Volume (shares)` ) %>%
  spread(teams, `Volume (shares)`)
names(trans_summary_volume) = c('hyp', 'Volume (Non-teams)', 'Volume (Teams)')
trans_summary_ntrans <- trans_summary %>%
  dplyr::select(hid, teams,`# Transactions` ) %>%
  spread(teams, `# Transactions`)
names(trans_summary_ntrans) = c('hyp', '# Transactions (Non-teams)', '# Transactions (Teams)')
trans_summary_ntraders <- trans_summary %>%
  dplyr::select(hid, teams,`# Traders` ) %>%
  spread(teams, `# Traders`)
names(trans_summary_ntraders) = c('hyp', '# Traders (Non-teams)', '# Traders (Teams)')

all_wide_df = join(join(join(trans_summary_ntraders, trans_summary_ntrans), trans_summary_volume), trans_summary_tokens) %>%
  rename(`Hyp #` = hyp)
all_wide_df = all_wide_df[c("Hyp #",
                       "Tokens invested (Non-teams)",
                       "Volume (Non-teams)",
                       "# Traders (Non-teams)",
                       "# Transactions (Non-teams)",
                       "Tokens invested (Teams)",
                       "Volume (Teams)",
                       "# Transactions (Teams)",
                       "# Traders (Teams)")]
                       
write.table(all_wide_df,
            file=paste(output_dir,
                  "Figures/SuppTable_MarketDetails.tsv",sep='/'),
            quote=FALSE, col.names=TRUE,sep='\t', row.names=FALSE)

```
 
 ### Expertise analyses
 
```{r expertiseSummary}
expertise <- read_csv(paste(basedir, "orig/PredictionMarkets/Demographics.csv", sep='/'))

expertise_summary <- expertise %>%
  group_by(teams) %>%
  summarise(mean_neuroimaging = mean(neuroimaging),
            sd_neuroimaging = sd(neuroimaging),
            mean_decision = mean(decisionsciences),
            sd_decision = sd(decisionsciences))
print(expertise_summary)
```
 
```{r expertiseTTest}
t.test.neuro <- t.test(neuroimaging ~ teams, data=expertise)
print(t.test.neuro)

t.test.decision <- t.test(decisionsciences ~ teams, data=expertise)
print(t.test.decision)

```

#### Payment anlaysis

```{r payoffExpertiseCorrs}

payoff.neuro <- cor.test(x=expertise$neuroimaging, 
                     y=expertise$payment, 
                     method='spearman', 
                     exact=FALSE)
print(payoff.neuro)

payoff.decision <- cor.test(x=expertise$decisionsciences, 
                     y=expertise$payment, 
                     method='spearman', 
                     exact=FALSE)
print(payoff.decision)

```

Separately for teams and non-teams

```{r payoffCorrTeams}
expertise_teams <- expertise %>% filter(teams==1)

payoff.neuro <- cor.test(x=expertise_teams$neuroimaging, 
                     y=expertise_teams$payment, 
                     method='spearman', 
                     exact=FALSE)
print(payoff.neuro)

payoff.decision <- cor.test(x=expertise_teams$decisionsciences, 
                     y=expertise_teams$payment, 
                     method='spearman', 
                     exact=FALSE)
print(payoff.decision)

```

```{r payoffCorrNonTeams}
expertise_nonteams <- expertise %>% filter(teams==0)

payoff.neuro <- cor.test(x=expertise_nonteams$neuroimaging, 
                     y=expertise_nonteams$payment, 
                     method='spearman', 
                     exact=FALSE)
print(payoff.neuro)

payoff.decision <- cor.test(x=expertise_nonteams$decisionsciences, 
                     y=expertise_nonteams$payment, 
                     method='spearman', 
                     exact=FALSE)
print(payoff.decision)

```
