---
title: "NARPS Prediction Market Analyses"
output:
  pdf_document: default
  html_notebook: default
---

This was adapted from Analyses.R provided by Felix Holzmeister.


## Setup Working Directories
```{r setup}

basedir = Sys.getenv('NARPS_BASEDIR')
if (basedir == ""){
  # use default
  basedir = "/data"
}
basedir = '/Users/poldrack/data_unsynced/NARPS_docker'

output_dir <- paste(basedir,'PredictionMarkets',sep='/')
proc <- paste(output_dir, 'Processed',sep='/')
if (!dir.exists(proc)){
  stop('proc dir does not exist!')
}


```

## Prepare Data

```{r prepareData}
load(paste(proc, "Prices.RData", sep='/'))
load(paste(proc, "Fundamentals.RData", sep='/'))

Data <- merge(Prices, 
              fundamental, 
              by="hid")

Data <- reshape(Data, 
                direction = "wide", 
                v.names = "price", 
                timevar = "teams", 
                idvar = "hid")


```



## SPEARMAN CORRELATIONS: MARKET BELIEFS

### Fundamental Value vs. Market Belief 'Non-Teams'

```{r}
sc_fv_nt <- cor.test(x=Data$price.0, 
                     y=Data$fv, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_fv_nt$estimate, 
    "p-value:", sc_fv_nt$p.value)

```



### Fundamental Value vs. Market Belief 'Teams'

```{r}
sc_fv_tt <- cor.test(x=Data$price.1, 
                     y=Data$fv, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_fv_tt$estimate, 
    "p-value:", sc_fv_tt$p.value)

```



# Market Belief 'Non-Teams' vs. Market Belief 'Teams' #
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #

```{r}
sc_nt_tt <- cor.test(x=Data$price.0, 
                     y=Data$price.1, 
                     method='spearman', 
                     exact=FALSE)
cat("rho:", sc_nt_tt$estimate, 
    "p-value:", sc_nt_tt$p.value)


```



### WILCOXON SIGNED-RANK TESTS: MARKET BELIEFS                                 ###
### -------------------------------------------------------------------------- ###

# Fundamental Value vs. Market Belief 'Non-Teams' #
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
```{r}
wt_fv_nt <- wilcox.test(Data$price.0, 
                        Data$fv, 
                        alternative="two.sided", 
                        paired=TRUE, 
                        exact=TRUE)
cat("z-value:", abs(qnorm(wt_fv_nt$p.value/2)), 
    "p-value:", wt_fv_nt$p.value)

```



# Fundamental Value vs. Market Belief 'Teams' #
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #

```{r}
wt_fv_tt <- wilcox.test(Data$price.1, 
                        Data$fv, 
                        alternative="two.sided",
                        paired=TRUE,
                        exact=TRUE) 
cat("z-value:", abs(qnorm(wt_fv_tt$p.value/2)), 
    "p-value:", wt_fv_tt$p.value)

```

# Market Belief 'Non-Teams' vs. Market Belief 'Teams' #
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ #
```{r}
wt_nt_tt <- wilcox.test(Data$price.0, 
                        Data$price.1, 
                        alternative="two.sided", 
                        paired=TRUE, 
                        exact=TRUE)  
cat("z-value:", abs(qnorm(wt_nt_tt$p.value/2)), 
    "p-value:", wt_nt_tt$p.value)


```




# Prepare Data #
# ~~~~~~~~~~~~ #

```{r}
load(paste(proc, "Holdings.RData", sep='/'))
load(paste(proc, "TeamResults.RData", sep='/'))
load(paste(proc, "Fundamentals.RData", sep='/'))

Data <- merge(Holdings,
              TeamResults,
              by=c("uid","hid","teams"),
              all.x = TRUE)

Data <- merge(Data, 
              fundamental, 
              by="hid")

Data<-Data[!(Data$teams == 0),]
Data<-Data[!(Data$shares == 0),]

```


### SPEARMAN CORRELATIONS: Fundamental Value vs. Market Belief 'Teams'         ###
### -------------------------------------------------------------------------- ###
```{r}
for (i in 1:9) {
  
  data_corr<-Data[(Data$hid == i),]

  corr <- cor.test(x=data_corr$shares, 
                   y=data_corr$decision,
                   method='spearman', 
                   exact=FALSE)
  
  cat("Hypothesis", i, ": \n",
      "  rho:    ", corr$estimate, "\n", 
      "  p-value:", corr$p.value, "\n",
      "\n\n")
  
}

```


### WILCOXON SIGNED-RANK TESTS: Final Holdings Consistent with Team Result     ###
### -------------------------------------------------------------------------- ###
```{r}

Data$consistent <- 0
Data$consistent <- ifelse(Data$decision==1 & Data$shares>0,1,Data$consistent)
Data$consistent <- ifelse(Data$decision==0 & Data$shares<0,1,Data$consistent)

for (i in 1:9) {
  
  data_wt <- Data[(Data$hid == i),]
  
  data_wt$testval <- 0.5
  data_wt$test <- data_wt$consistent - 0.5
  a <- as.data.frame(table(sign(data_wt$test)))
  
  a$total <- sum(a$Freq)
  a$frac  <- a$Freq/a$total
  
  wt <- wilcox.test(data_wt$consistent, 
                    data_wt$testval, 
                    alternative="two.sided",
                    paired=TRUE,
                    exact=FALSE)      
  
  fv <- mean(data_wt$fv)
  z <- abs(qnorm(wt$p.value/2))
  inc <- mean(data_wt[data_wt$consistent==0,"shares"])
  con <- mean(data_wt[data_wt$consistent==1,"shares"])
  frac <- a[a$Var1==1, "frac"]
  
  cat("Hypothesis", i, ": \n",
      "  consistent:                    ", frac, 
      "  ( z =", z, ", p =", wt$p.value, ")", "\n",
      "  fundamental value:             ", fv, "\n",
      "  avg. holdings if consistent:   ", con, "\n",
      "  avg. holdings if inconsistent: ", inc, "\n",
      "\n\n")

}


```




# Prepare Data #
# ~~~~~~~~~~~~ #
```{r}

load(paste(proc, "BalancedPanel.Rdata", sep='/'))
#attach(BalancedPanel, warn.conflicts = FALSE)


### PANEL REGRESSIONS                                                          ###
### -------------------------------------------------------------------------- ###
m1 <- lm(ae~time+teams, data = BalancedPanel)
summary(m1, robust=TRUE)

m2 <- lm(ae~time+teams+time:teams, data = BalancedPanel)
summary(m2, robust=TRUE)

```
